The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-06 eswc-2012/workshop2.tex
why hypermedia RDF
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@163 43ef1190-90fd-4dd7-a769-d0121f02b80e
contrast graphstore
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@164 43ef1190-90fd-4dd7-a769-d0121f02b80e

Semantic Web services are likely to be an important source of data for
future applications, but for foreseeable future they are just one of many. A
key promise of the Semantic Web is the ability to integrate many data
sources easily. There are two key issues, first read-write operations
must be similar to how it is done with other hypermedia types, to make
it possible to use generic code to minimize the effort required to
support RDF. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.

@@

We see that with a simple vocabulary, RDF serializations can become a
very powerful hypermedia types. We also note that this vocabulary
enables agents to do the same operations as the SPARQL 1.1 Graph Store
HTTP
Protocol\footnote{\url{http://www.w3.org/TR/2011/WD-sparql11-http-rdf-update-20110512/}},
while being fully RESTful. The Protocol specification is currently not RESTful
per the discussion above, even though it was a key design goal. It
should also be possible to use this on the default (nameless) graph by
assigning it a name in the service description rather than defining it
in an out-of-band specification like is currently being done.

>>>>

Semantic Web services are likely to be an important source of data for
future applications, but for foreseeable future they are just one of many. A
key promise of the Semantic Web is the ability to integrate many data
sources easily. There are two key issues, first read-write operations
must be similar to how it is done with other hypermedia types, to make
it possible to use generic code to minimize the effort required to
support RDF. Importantly, if interacting with Linked Data requires
extensive out-of-band information, it will be harder to use than media
types that does not. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.

@@

We see that with a simple vocabulary, RDF serializations can become a
very powerful hypermedia types. We also note that this vocabulary
enables agents to do the same operations as the SPARQL 1.1 Graph Store
HTTP
Protocol\footnote{\url{http://www.w3.org/TR/2011/WD-sparql11-http-rdf-update-20110512/}},
while being fully RESTful. The Protocol specification is currently not RESTful
per the discussion above as it requires extensive out-of-band information, even though it was a key design goal. It
should also be possible to use this on the default (nameless) graph by
assigning it a name in the service description rather than defining it
in an out-of-band specification like is currently being done.
